---
title: "0412_adt_01"
author: "180212_my"
date: "2018??? 4??? 12???"
output: html_document
---

## load libraries
```{r}
install.packages(c('data.table', 'DT', 'magrittr', 'corrplot', 'Rmisc', 'ggalluvial', 'caret', 'ModelMetrics', 'scales', 'irlba', 'forcats', 'forecast', 'TSA', 'zoo', 'gridExtra', 'sqldf', 'xgboost'))

## load packages
library(data.table)
library(sqldf)
library(ggplot2)
library(gridExtra)
library(caret)
library(dplyr)
library(lubridate)  # time 
library(xgboost)

#remove.packages("plotROC")
#install.packages('plotROC', dep = TRUE)
```

## set the data path
```{r}
# getwd()
train_path <- "../data/ad.tracking/train_10m.csv"
train_sample_path <- "../data/ad.tracking/train_sample.csv"
test_path  <- "../data/ad.tracking/test.csv"
```

## load dataset
```{r}
train <- fread(train_path, showProgress = F, stringsAsFactors = F, na.string=c("", NA))
df <- fread(train_sample_path, showProgress = F, stringsAsFactors = F, na.string=c("", NA))
test <- fread(test_path, showProgress = F, stringsAsFactors = F)

set.seed(0)
train <- train[sample(.N, 1e6), ]
```

```{r}
head(train)
head(test)
```

```{r}
str(train)
str(test)
```

```{r}
summary(train)
```

```{r}
dim(train) ; dim(test)
```

```{r}
colnames(train)
colnames(test)
```

## Missing value checking
```{r}
colSums(is.na(train)) # 997495 missing value = number of not-downloaded 
colSums(is.na(test))  ## no missing value in test dataset
```

## Convert click_time into proper date & time format
```{r}
# Click time
cl_ymd <- ymd(as.Date(train$click_time))
cl_year <- year(cl_ymd)
cl_month <- month(cl_ymd)
cl_day <- day(cl_ymd)
cl_hour <- as.POSIXlt(train$click_time)$hour
cl_min <- as.POSIXlt(train$click_time)$min
cl_sec <- as.POSIXlt(train$click_time)$sec

# Attributed time
at_ymd <- ymd(as.Date(train$attributed_time))
at_year <- year(at_ymd)
at_month <- month(at_ymd)
at_day <- day(at_ymd)
at_hour <- as.POSIXlt(train$attributed_time)$hour
at_min <- as.POSIXlt(train$attributed_time)$min
at_sec <- as.POSIXlt(train$attributed_time)$sec

tr2 <- cbind(train, cl_year, cl_month, cl_day, cl_hour, cl_min, cl_sec, at_year, at_month, at_day, at_hour, at_min, at_sec)
# df2 <- cbind(df, cl_year, cl_month, cl_day, cl_hour, cl_min, cl_sec)
tr2 <- tr2 %>% select(-c(click_time, attributed_time, cl_year, cl_month, at_year, at_month))
head(tr2)

```

## Check the unique number for each of feature
```{r}
length(t_ip)     # 34857 (100000-34857)
length(t_app)    # 161
length(t_device) # 100
length(t_os)     # 130
length(t_chl)    # 161

# OR
unique <- as.data.frame(apply(tr2[,1:7], 2, function(x) length(unique(x)))) # 1: row 2: column
```


## Unique values by each features
```{r}
unique <- as.data.frame(apply(tr2[,1:7], 2, function(x) length(unique(x))))
unicount <- transpose(unique)
colnames(unicount) <- c('ip', 'app', 'device', 'os', 'channel', 'click_time', 'attributed_time')  
  
unicount %>%
  melt(variable.name = "features", value.name = "unique_values") %>%
  ggplot(aes(reorder(features, -unique_values), unique_values)) +
  geom_bar(stat ="identity", fill="steelblue") + 
  scale_y_log10(breaks = c(150,300, 500, 1000, 50000, 100000)) +
  geom_text(aes(label = unique_values), vjust = 1.6, color = "white", size=3.5) +
  theme_minimal() +
  labs(x = "features", y = "Number of unique values")
```


## Top 10 OS by ¡®is_attributed¡¯
```{r}
os1 <- tr2[tr2$is_attributed == "0", ][, .N, by = os][order(-N)][1:10] %>%
  ggplot(aes(reorder(os, -N), N)) +
  geom_bar(stat='identity', fill="steelblue") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=1.5, color="white", size=3) +
  ggtitle("Top 10 OS by number of no downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("os") +
  ylab("numbers of no downloads")

os2 <- tr2[tr2$is_attributed == "1", ][, .N, by = os][order(-N)][1:10] %>%
  ggplot(aes(reorder(os, -N), N)) +
  geom_bar(stat='identity', fill="pink2") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=1.5, color="white", size=3) +
  ggtitle("Top 10 OS by number of downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("os") +
  ylab("numbers of downloads")

ggarrange(os1, os2, nrow=2)
```


## Top 10 App by ¡®is_attributed¡¯
```{r}
app1 <- tr2[tr2$is_attributed == "0", ][, .N, by = app][order(-N)][1:10] %>%
  ggplot(aes(reorder(app, -N), N)) +
  geom_bar(stat='identity', fill="steelblue") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=.5, color="black", size=3) +
  ggtitle("Top 10 App by number of no downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("app") +
  ylab("numbers of no downloads")

app2 <- tr2[tr2$is_attributed == "1", ][, .N, by = app][order(-N)][1:10] %>%
  ggplot(aes(reorder(app, -N), N)) +
  geom_bar(stat='identity', fill="pink2") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=.5, color="black", size=3) +
  ggtitle("Top 10 App by number of downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("app") +
  ylab("numbers of downloads")

ggarrange(app1, app2, nrow=2)
```


## Top 10 Device by ¡®is_attributed¡¯
```{r}
dv1 <- tr2[tr2$is_attributed == "0", ][, .N, by = device][order(-N)][1:10] %>%
  ggplot(aes(reorder(device, -N), N)) +
  geom_bar(stat='identity', fill="steelblue") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=+.1, color="black", size=3) +
  ggtitle("Top 10 Device by number of no downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("device") +
  ylab("numbers of no downloads")

dv2 <- tr2[tr2$is_attributed == "1", ][, .N, by = device][order(-N)][1:10] %>%
  ggplot(aes(reorder(device, -N), N)) +
  geom_bar(stat='identity', fill="pink2") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=+.1, color="black", size=3) +
  ggtitle("Top 10 Device by number of downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("device") +
  ylab("numbers of downloads")

ggarrange(dv1, dv2, nrow=2)
```


## Top 10 Channel by ¡®is_attributed¡¯
```{r}
chl1 <- tr2[tr2$is_attributed == "0", ][, .N, by = channel][order(-N)][1:10] %>%
  ggplot(aes(reorder(channel, -N), N)) +
  geom_bar(stat='identity', fill="steelblue") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=+.5, color="black", size=3) +
  ggtitle("Top 10 Channel by number of no downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("channel") +
  ylab("numbers of no downloads")

chl2 <- tr2[tr2$is_attributed == "1", ][, .N, by = channel][order(-N)][1:10] %>%
  ggplot(aes(reorder(channel, -N), N)) +
  geom_bar(stat='identity', fill="pink2") +
  theme_minimal() +
  geom_text(aes(label=N), vjust=+.5, color="black", size=3) +
  ggtitle("Top 10 Channel by number of downloads") +
  theme(plot.title = element_text(hjust=0.5)) +
  xlab("channel") +
  ylab("numbers of downloads")

ggarrange(chl1, chl2, nrow=2)
```


## ggplot - click_time VS attributed_time by hour
```{r}

#install.packages("ggpubr")
library(ggpubr)

p1 <- ggplot(tr2, aes(x=cl_hour)) + 
  geom_bar(fill="steelblue") +
  ggtitle("Number of clicks per hour") +
  xlab("Hour") +
  ylab("Number of clicks") +
  theme_minimal()

p2 <- ggplot(tr2, aes(x=at_hour)) + 
  geom_bar(fill="pink2") +
  ggtitle("Number of downloads per hour") +
  xlab("Hour") +
  ylab("Number of downloads") +
  theme_minimal()

ggarrange(p1, p2)
```

## ggplot - click_time VS attributed_time by day
```{r}
p3 <- ggplot(tr2, aes(x=cl_day)) + 
  geom_bar(fill="steelblue") +
  ggtitle("Number of clicks per day") +
  xlab("Day") +
  ylab("Number of clicks") +
  theme_minimal()

p4 <- ggplot(tr2, aes(x=at_day)) + 
  geom_bar(fill="pink2") +
  ggtitle("Number of downloads per day") +
  xlab("Day") +
  ylab("Number of downloads") +
  theme_minimal()

ggarrange(p3, p4)
```

## converting > categorical variables
```{r}
names <- c('ip', 'app', 'device', 'os', 'channel', 'is_attributed', 'cl_day', 'cl_hour')
tr3 <- tr2
setDF(tr2) # convert to data.frame

tr3[names] <- lapply(tr3[names], as.factor)
str(tr3)
```

## Correlation between features
```{r}
options(repr.plot.width=6, repr.plot.height=6)
install.packages('ggcorrplot')
library(ggcorrplot)
tr2$is_attributed <- as.integer(tr2$is_attributed)
train_cor <- round(cor(tr2[,c(1:8)]), 1)

ggcorrplot(train_cor,  title = "Correlation")+theme(plot.title = element_text(hjust = 0.5))
```
